Pillar 1 - Sequential Pattern Mining

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
consistent format

# Probability of taking a course
d_support$TNT <- d_transactions$taken_PF_HL %>%
  distinct(
    item,
    sequenceID
    ) %>%
  count(
    item
    ) %>%
  mutate(
    rate.take = n / n_students,
    rate.not  = 1 - rate.take
    )

>>>>

#
# Probability of taking a course
d_support$TNT <- d_transactions$taken_PF_HL %>%
  distinct(
    item,
    sequenceID
    ) %>%
  count(
    item
    ) %>%
  mutate(
    rate.take = n / n_students,
    rate.not  = 1 - rate.take
    )
